Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-21 cloneoverflow-latex/cloneoverflow.tex
Updated latex

	\caption{58 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}

@@

	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{r|l|l|l|l|c|l}

@@

		No. & Project & File & License & SO Post & Changes & Date \\

@@

			1 & aspectj-1.6.9  & Agent.java  & -- & 18303692 & alteration  & 2015-09-08 \\
			2 & aspectj-1.6.9  & Agent.java  & -- & 18303692 & alteration  & 2015-09-08 \\
			3 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1 & 2513183 & alteration  &  2015-03-17 \\
			4 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
			5 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
			6 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  & 2011-03-01 \\
			7 & eclipse-SDK  & WizardDialog.java  & EPLv1  &   11861598	 & alteration  &  2011-02-03 \\
			8 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
			9 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & Apache-2 & 14845581 & alteration  & 2012-06-25 \\
			11 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
			12 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
			13 & hadoop-1.0.0  & StringUtils.java  & Apache-2 & 801987 & alteration  & 2013-02-04 \\
			14 & hadoop-1.0.0  & TestJobCounters.java  & Apache-2 & 18833798 & alteration  & 2011-06-12 \\
			15 & hadoop-1.0.0  & TextOutputFormat.java  & Apache-2 & 16928749 & alteration  & 2011-06-12 \\
			16 & hadoop-1.0.0  & WritableComparator.java  & Apache-2 & 22315734 & alteration  & 2014-11-20 \\
			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & -- & 15168494 & alteration  & 2012-06-24 \\
			18 & hibernate-4.2.2  & Example.java  & -- & 24924255 & alteration  & 2013-04-23 \\
			19 & hibernate-4.2.2  & SchemaUpdate.java  & -- & 23520731 & alteration  & 2016-02-05 \\
			20 & hibernate-4.2.2  & SettingsFactory.java  & -- & 8257554 & removal  & 2011-03-11 \\
			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & -- & 23967852 & alteration  & 2015-03-12 \\
			22 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2008-04-17 \\
			23 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2011-05-20 \\
			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & GLGPLv2.1+ & 12936580 & alteration  & 2016-02-19 \\
			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & GLGPLv2.1+ & 16058183 & alteration  & 2013-07-03 \\
			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
			28 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			29 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			30 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			31 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			32 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 14940863 & alteration  & 2015-12-13 \\
			33 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 24680923 & alteration  & 2015-12-13 \\
			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
			36 & junit-4  & Assert.java  & -- & 23586872 & alteration  & 2015-05-12 \\
			37 & junit-4  & ExternalResource.java  & -- & 7504040 & alteration  & 2016-06-25 \\
			38 & junit-4.11  & ExpectException.java  & -- & 8802082 & alteration  & 2014-05-26 \\
			39 & poi-3.6-20091214  & WorkbookFactory.java  & Apache-2 & 12593810 & alteration  & 2015-04-29 \\
			40 & spring-framework-3.0.5  & AnnotationMethodHandlerExceptionResolver.java  & Apache-2 & 5660519 & removal  & 2012-01-20 \\
			41 & spring-framework-3.0.5  & AutowireUtils.java  & Apache-2 & 20913543 & alteration  & 2014-10-28 \\
			42 & spring-framework-3.0.5  & CustomCollectionEditor.java  & Apache-2 & 18623736 & alteration  & 2013-11-21 \\
			43 & spring-framework-3.0.5  & DefaultAnnotationHandlerMapping.java  & Apache-2 & 3758110 & removal  & 2012-01-20 \\
			44 & spring-framework-3.0.5  & DefaultPropertiesPersister.java  & Apache-2 & 6149818 & alteration  & 2013-03-19 \\
			45 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2016-07-15 \\
			46 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
			47 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
			48 & spring-framework-3.0.5  & DispatcherServlet.java  & Apache-2 & 4781746 & alteration  & 2011-08-08 \\
			49 & spring-framework-3.0.5  & Jaxb2Marshaller.java  & Apache-2 & 10924700 & alteration  & 2012-08-28 \\
			50 & spring-framework-3.0.5  & ScheduledTasksBeanDefinitionParser.java  & Apache-2 & 3751463 & alteration  & 2016-07-05 \\
			51 & struts2-2.2.1  & DefaultActionMapper.java  & Apache-2 & 14019840 & alteration  & 2013-10-18 \\
			52 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
			53 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
			54 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
			55 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
			56 & tomcat-7.0.2  & FormAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
			57 & tomcat-7.0.2  & HttpServlet.java  & Apache-2 & 5266856 & alteration  & 2011-10-22 \\
			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & Apache-2 & 10289462 & alteration  & 2012-09-12 \\

@@

}

@@

\subsubsection{Software licensing violation}
Software licensing is a paramount factor in software development. Violation of software license can cause a major impact to the delivery of the software and also lead to legal issues. It is an emerging area that software engineering research community is paying attention to. For example, there are studies of automatic technique to identify software licensing from source code files \cite{German2010} and the evolution of licenses in open source projects \cite{DiPenta2010}.

>>>>

	\caption{58 code clones in Stack Overflow (SO) that were altered, rewritten, or removed from the project after posted and their respective licenses. Files can be changed ($C$) by modifications ($M$), deletion ($D$), and rewriting ($R$).}

@@

	\scriptsize
%	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|c|l}

@@

		No. & Project & File & Start & End & License & SO No. & $C$ & C$_{\textit{\textrm{date}}}$ \\

@@

			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & $M$  &  2015-03-17 \\
			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	 & $M$  & 2011-03-01 \\
			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	 & $M$  &  2011-02-03 \\
			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & $M$  & 2012-06-25 \\
			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & $M$  & 2013-02-04 \\
			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & $M$  & 2011-06-12 \\
			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & $M$  & 2011-06-12 \\
			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & $M$  & 2014-11-20 \\
			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & $M$  & 2012-06-24 \\
			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & $M$  & 2013-04-23 \\
			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & $M$  & 2016-02-05 \\
			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & $D$  & 2011-03-11 \\
			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & $M$  & 2015-03-12 \\
			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & GLGPLv3+ & 8037824 & $M$  & 2008-04-17 \\
			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & GLGPLv3+ & 8037824 & $M$  & 2011-05-20 \\
			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & GLGPLv2.1+ & 12936580 & $M$  & 2016-02-19 \\
			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & GLGPLv2.1+ & 16058183 & $M$  & 2013-07-03 \\
			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & $M$  & 2015-12-13 \\
			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & $M$  & 2015-12-13 \\
			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & $M$  & 2010-04-13 \\
			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & $M$  & 2010-04-13 \\
			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & $M$  & 2015-05-12 \\
			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & $M$  & 2016-06-25 \\
			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & $M$  & 2014-05-26 \\
			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & $M$  & 2015-04-29 \\
			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & $D$  & 2012-01-20 \\
			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & $M$  & 2014-10-28 \\
			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & $M$  & 2013-11-21 \\
			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & $D$  & 2012-01-20 \\
			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & $M$  & 2013-03-19 \\
			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2016-07-15 \\
			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
			47 & spring-3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
			48 & spring-3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & $M$  & 2011-08-08 \\
			49 & spring-3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & $M$  & 2012-08-28 \\
			50 & spring-3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & $M$  & 2016-07-05 \\
			51 & struts2-2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & $M$  & 2013-10-18 \\
			52 & tomcat-7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
			53 & tomcat-7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
			54 & tomcat-7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & $M$  & 2012-11-18 \\
			55 & tomcat-7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & $M$  & 2012-11-18 \\
			56 & tomcat-7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
			57 & tomcat-7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & $M$  & 2011-10-22 \\
			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & $M$  & 2012-09-12 \\

@@

%}

@@

\subsubsection{Software licensing violation}
Software licensing is a paramount factor in software development. Violation of software license can cause a major impact to software delivery and also lead to legal issues. It is an emerging area that software engineering research community is paying attention to. For example, there are studies of automatic technique to identify software licensing from source code files \cite{German2010} and the evolution of licenses in open source projects \cite{DiPenta2010}.
